% ==================== ABSTRACT ====================
% STYLE GUIDELINES:
% - 150-250 words summarizing: objective, methodology, results, conclusions
% - Included in table of contents: NO (preliminary page)
% - Must include 5-7 keywords relevant to the project
% - Keywords should be scientifically relevant for academic databases
% - Font: Times New Roman 12pt, line spacing 1.5, justified text
% ====================================================================
\phantomsection
\thispagestyle{plain}
\begin{center}
{\huge\bfseries Abstract}
\end{center}
\addcontentsline{toc}{chapter}{Abstract}


\initial{T}his report presents IoT-REAP, a secure industrial remote operations platform for Industry 4.0. The platform addresses challenges in remote access, such as VPN complexity, session management, and OT/IT network isolation.

Developed with Laravel, React, TypeScript, and Python FastAPI, IoT-REAP integrates Proxmox VE for VM provisioning, Apache Guacamole for browser-based remote desktop, and MQTT for IoT robot control. Innovations include zero-trust security, device fingerprinting, geo-IP anomaly detection, real-time risk scoring, AI-powered demand forecasting, and predictive maintenance.

The system supports 50+ concurrent users with automatic VM provisioning, sub-200ms robot telemetry latency, and tamper-proof audit logging for IEC 62443 compliance. Results show secure, browser-based access to industrial systems with no client installation.

\vspace{0.5cm}
\noindent\textbf{Keywords:} Industry 4.0, IoT, Remote Access, Proxmox VE, Apache Guacamole, MQTT, Zero-Trust Security, IEC 62443, Predictive Maintenance, Machine Learning

\vspace{0.9cm}

\begin{center}
{\huge\bfseries Résumé}
\end{center}


\initial{C}e rapport présente IoT-REAP, une plateforme sécurisée d'opérations industrielles à distance pour l'Industrie 4.0. Elle répond aux défis de l'accès distant, comme la complexité des VPN, la gestion des sessions et l'isolation des réseaux OT/IT.

Développée avec Laravel, React, TypeScript et Python FastAPI, IoT-REAP intègre Proxmox VE pour le provisionnement de VM, Apache Guacamole pour l'accès bureau à distance, et MQTT pour le contrôle de robots IoT. Les innovations incluent la sécurité zero-trust, empreinte d'appareil, détection d'anomalies géo-IP, scoring de risque, prévision de demande par IA et maintenance prédictive.

Le système supporte plus de 50 utilisateurs simultanés avec provisionnement automatique de VM, latence de télémétrie robot <200ms, et journalisation d'audit inviolable pour la conformité IEC 62443. Les résultats montrent un accès sécurisé, via navigateur, aux systèmes industriels sans installation client.

\vspace{0.5cm}
\noindent\textbf{Mots-clés:} Industrie 4.0, IoT, Accès à Distance, Proxmox VE, Apache Guacamole, MQTT, Sécurité Zero-Trust, IEC 62443, Maintenance Prédictive, Apprentissage Automatique

\cleardoublepage