% ==================== CONCLUSION ====================
% STYLE GUIDELINES:
% - Maximum 2 pages (750 words maximum)
% - Summarize work carried out and main contributions
% - Highlight difficulties encountered
% - Propose prospects for future development
% - If a section has subsections, add a short descriptive paragraph immediately after the parent heading before the first subsection.
% - Font: Times New Roman 12pt, line spacing 1.5
% - Section titles: left-aligned, bold (if used)
% ====================================================================
\phantomsection
{\huge\bfseries General Conclusion}
\addcontentsline{toc}{chapter}{General Conclusion}
\vspace{1cm}

\initial{A}s part of our internship at Novation City, we designed and implemented IoT-REAP, a secure industrial remote operations and training platform built to support Industry 4.0 learning and experimentation. The main objective was to reduce the dependency on physical presence in specialized laboratories by allowing engineers, teachers, and administrators to collaborate through one web platform that combines virtual machines, remote desktop access, camera supervision, and IoT device interaction. Instead of treating learning content and operational infrastructure as separate systems, we worked on a unified environment where users can launch sessions, access equipment, follow learning paths, and monitor activity from a single interface.

Our development approach was iterative and architecture-driven. On the backend, we relied on Laravel and organized the application around clear layers: validation through FormRequests, thin controllers, business logic in services, and data access through repositories. On the frontend, we used React with TypeScript to build reusable components and typed API integrations, which improved maintainability as the project expanded. We also enforced role-based flows for Engineer, Teacher, and Admin users so each profile sees only relevant actions and data. This structure gave us a strong foundation to integrate complex external systems while keeping the codebase understandable and extensible.

One of our major contributions was the implementation of the remote lab session lifecycle. We integrated Proxmox for VM provisioning and lifecycle control, allowing users to reserve and launch practical environments on demand. We coupled this with Guacamole-based browser access so sessions can be opened directly through RDP, VNC, or SSH without requiring local client installation. We implemented tokenized access patterns, expiration-aware session handling, and cleanup mechanisms to avoid orphaned resources and maintain platform stability. As a result, IoT-REAP provides a practical bridge between cloud orchestration and hands-on industrial training workflows.

Another major contribution was the integration of real-time hardware context into the learning experience. Through camera services and gateway integrations, users can observe equipment remotely while working in virtual sessions. We connected PTZ operations to MQTT-driven command channels, making it possible to control compatible devices from the platform while keeping command routing structured and auditable. We also developed USB device reservation and assignment workflows so specific hardware can be attached to active training sessions in a controlled way. This combination of VM access, live observation, and device interaction moves the platform beyond a traditional e-learning portal and closer to an operational remote laboratory.

Beyond infrastructure access, we contributed to the educational layer by supporting training path management and instructor workflows. Teachers can prepare structured learning content, and learners can progress through guided material connected to practical sessions. This alignment between pedagogical structure and technical execution is a key value of IoT-REAP: users do not only read about industrial systems, they interact with realistic environments while following organized training objectives. We also improved API organization and frontend consumption patterns so core educational and operational features evolve together instead of diverging over time.

The project also exposed significant engineering difficulties. The first challenge was integrating heterogeneous technologies with different operational behaviors: Proxmox operations are asynchronous, remote desktop tunnels are state-sensitive, MQTT control requires consistent topic discipline, and camera streaming introduces network variability. Coordinating these elements in a reliable user experience required careful service abstraction, robust error handling, and continuous end-to-end verification. We addressed this by isolating external provider logic in dedicated services, standardizing integration points, and improving observability through explicit logs and defensive checks.

The second challenge involved preserving architectural quality while feature scope grew rapidly. As new modules were added, keeping controllers thin, preventing business logic leakage across layers, and maintaining typed frontend contracts required constant discipline. We handled this by enforcing coding patterns, documenting API gaps, and prioritizing incremental refactoring where necessary. This process highlighted an important practical lesson: in real-world platforms, maintainability must be treated as a deliverable, not as a post-project cleanup activity.

The third challenge was balancing delivery speed with security and reliability requirements. Because IoT-REAP handles privileged operations such as VM control, remote access, and hardware assignment, authorization boundaries had to be explicit and testable. We reinforced validation and role checks, improved ownership scoping on sensitive actions, and added focused regression tests for security-critical paths. Combined with linting, type checks, and unit/feature testing practices, this gave us a higher-confidence development workflow and reduced the risk of silent regressions during rapid iteration.

Looking forward, several development prospects can further strengthen the platform. A first priority is to complete the remaining high-impact API integrations and user-flow parity, especially where advanced admin and teaching operations still need richer frontend exposure. A second prospect is deeper analytics for session usage, infrastructure efficiency, and learner progression, enabling more data-driven operational decisions. A third prospect is predictive scheduling and smarter resource allocation to reduce wait times and improve capacity planning. Additional opportunities include strengthened zero-trust controls, compliance-oriented audit reporting, and mobile-oriented access improvements for better field usability.

From a professional perspective, this internship significantly accelerated our growth as software engineers. We gained practical experience in full-stack architecture, distributed integration, security-aware design, and collaborative delivery under evolving requirements. We also learned how to transform audit feedback and roadmap constraints into actionable technical decisions. Most importantly, we understood that impactful engineering is not only about implementing features, but about building systems that remain reliable, secure, and adaptable as complexity increases.

In conclusion, the IoT-REAP project represents a meaningful contribution to Novation City's digital industrial training vision. We delivered a strong technical foundation that connects virtual infrastructure, remote interaction, and structured learning in one coherent platform. While important evolution paths remain, the current system already demonstrates the feasibility and value of remote Industry 4.0 training at scale. We are proud of the progress achieved during this internship and motivated to continue improving the platform so it can serve as a durable reference for secure, practical, and modern industrial education.

\cleardoublepage